EDIpack2: interoperable Lanczos-based solver for generic quantum impurity problems

### 2025-05-18 05_examples.tex

One of the features introduced in \NAME is the possibility of treating local phonons in the superconductive case (i.e. \textbf{ed\_mode=superc} ). In this example we show how to get the normal and superconductive solutions of the Holstein model on the Bethe lattice within DMFT. The phononic and electron-phonon part of the Holstein hamiltonian at half-filling for particle-hole symmetric density of states like in the Bethe lattice reads:
\begin{equation} \label{eqex:H_Holstein}
    H_{int} = \sum_i \Big[\omega_0 b^\dagger_i b_i + g(b^\dagger_i + b_i)\sum_{\sigma}(c^\dagger_{i\sigma}c_{i\sigma} -\frac{1}{2})\Big]
\end{equation}

>>>>

One of the features introduced in \NAME is the possibility of treating local phonons in the superconductive case (i.e. \textbf{ed\_mode=superc} ). In this example we show how to get the normal and superconductive solutions of the Holstein model on the Bethe lattice within DMFT. The phononic and electron-phonon part of the Holstein Hamiltonian at half-filling for particle-hole symmetric density of states like in the Bethe lattice reads:
\begin{equation} \label{eqex:H_Holstein}
    H_{int} = \sum_i \Big[\omega_0 b^\dagger_i b_i + g(b^\dagger_i + b_i)\sum_{\sigma}(c^\dagger_{i\sigma}c_{i\sigma} -\frac{1}{2})\Big]
\end{equation}
